---
title: "Week 5 Day 2 Homework"
output: html_notebook
---


# Read in Libraries
```{r}
library(CodeClanData)
library(tidyverse)
```

# Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

## Thoughts
backpack - 100 rows, 9 columns
sex and major is a factor
Rest are numeric

```{r}
backpack <- backpack
glimpse(backpack)
```
```{r}
my_theme <- theme_classic() +
  theme(panel.grid.minor = element_line(colour = "grey60"),
        axis.title = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5))
```


# Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

## Thoughts
Create a histogram showing the nornmal distribution of the backpack weights (lbs has been set as the unit of weight for general discussion purposes,)

## Code and output
```{r}
backpack %>% 
ggplot(aes(x = backpack_weight)) +
  geom_histogram(binwidth = 1,
                 fill = "seagreen",
                 colour = "black") +
  labs(title = "Distribution of Backpack Weight",
       x = "Backpack Weight (lbs)") +
  scale_x_continuous(breaks = seq(1, max(backpack$backpack_weight), 2)) +
  my_theme
  

  #scale_fill_manual(values = c("seagreen")) +
  #theme_classic()
```
## Output Discussion
The median backpack weight it about 10lbs, there are some outliers above
23lbs.The distribution tends to be skewed to the left (lower weights)


# Question 3.

Are there differences in backpack weight between sex?

## Thoughts
Possible plot could be to have two histograms
for males and females.

## Code and output
```{r}

backpack %>% 
ggplot(aes(x = backpack_weight)) +
  geom_histogram(binwidth = 1,
                 aes(fill = sex,
                 ), colour = "black",
                 show.legend = FALSE) +
  labs(title = "Distribution of Backpack Weight",
       x = "Backpack Weight (lbs)") +
  facet_wrap(~ sex)+
  scale_y_continuous(expand = c(0,0)) + #breaks = seq(1, max(backpack$backpack_weight), 2)) +
  my_theme
```

## Discussion
The females tend to have lighter bags than the males within the data set. The 
general trend of the distribution is fairly similar but has more outlier on the
male size.



# Question 4.

What is the relationship between body weight and backpack weight?

## Thought
Create a scatter plot showing the body weight vs back pack.

## Code and output
```{r}
backpack %>% 
  ggplot(aes(x = body_weight,
             y = backpack_weight)) +
  geom_point() +
  geom_smooth(method = "lm", show.legend = FALSE) +
  my_theme+
  labs(title = "Backpack vs Bodyweight",
       x = "Body Weight (lbs)",
       y = "Back pack weight (lbs)")
```

## Discussion
From the plot there does not appear to be a trend between backpack weight and
body weight.


# Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

## Thoughts
Could complete similar plot to question 5. Possibly include in one chart with
shape and 

## Code and output

```{r}
backpack %>% 
  ggplot(aes(x = body_weight,
             y = backpack_weight)) +
  geom_point(aes(shape = sex,
                 colour = sex),
             size = 4) +
  geom_smooth(aes(colour = sex),
              method = "lm", show.legend = FALSE) +
  my_theme+
  labs(title = "Backpack vs Bodyweight for Males and Females",
       x = "Body Weight (lbs)",
       y = "Back pack weight (lbs)")
```
```{r}
backpack %>% 
  ggplot(aes(x = body_weight,
             y = backpack_weight,
             colour = sex)) +
  geom_point(show.legend = FALSE) +
  geom_smooth(method = "lm", show.legend = FALSE) +
  my_theme+
  labs(title = "Backpack vs Bodyweight for Males and Females",
       x = "Body Weight (lbs)",
       y = "Back pack weight (lbs)") +
  facet_wrap(~ sex)
```

# Discussion
There could be a possible steeper gradient of a linear trendline
for females. However this is still unlikely has a very low match with both
sets showing a large spread for the results. The only information shown is
that males are generally heavier than females- and this plot is not a good way
to show this.
 
# Question 6.

What proportion of students report back pain?

## Thoughts
Simple bar chart or column chart showing the amount of students

## Code and Output
```{r}
backpack %>% 
  group_by(back_problems) %>% 
  summarise(percent = 100* n() / nrow(backpack)) %>% 
  mutate(temp_var = 1) %>% 
  ggplot(aes(x = temp_var,
             y = percent,
             fill = factor(back_problems) == 1)) +
  geom_col() +
  scale_fill_manual(values = c("Purple", "Orange")) +
  #scale_fill_distiller(palette = "Dark2") +
  geom_text(aes(label = paste0(percent, "%")),
            position = position_stack(vjust = 0.5)) +
  theme_minimal() +
  scale_x_continuous(name = "", breaks = c()) +
  labs(title = "Students with Back Problems",
       y = "Percentage",
       fill = "Back Problems")

backpack %>% 
  group_by(back_problems) %>% 
  summarise(percent = 100* n() / nrow(backpack)) %>% 
  ggplot(aes(x = back_problems,
             y = percent,
             fill = factor(back_problems))) +
  geom_col(show.legend = FALSE) +
  scale_fill_manual(values = c("Purple", "Orange")) +
  #scale_fill_distiller(palette = "Dark2") +
  geom_text(aes(label = paste0(percent, "%")),
            position = position_stack(vjust = 0.5)) +
  theme_minimal() +
  scale_x_continuous(name = "", breaks = c()) +
  labs(title = "Students with Back Problems",
       y = "Percentage")
  
```
## Discussion
Around a third of students have reported back problems.

# Question 7.

Is this proportion different between men and women?

## Thoughts
Complete similar to before but use

```{r}
backpack %>% 
  group_by(back_problems, sex) %>% 
  summarise(count_num = n()) %>% 
  group_by(sex) %>% 
  mutate(percent = round(100*count_num/sum(count_num), 0)) %>% 
  mutate(back_problems = if_else(back_problems == 1, "Issue", "No Issue")) %>% 
  ggplot(aes(x = sex,
             y = percent,
             fill = factor(back_problems))) +
  geom_col() +
  scale_fill_manual(values = c("Purple", "Orange"))+ #scale_fill_distiller(palette = "Dark2") +
  geom_text(aes(label = paste0(percent, "%")),
            position = position_stack(vjust = 0.5)) +
  my_theme +
  labs(title = "Students with Back Problems-Males and Females",
       y = "Percentage",
       x = "Sex",
       fill = "Back Problems")
```

## Discussion
Women tend to have more back problems than men with an almost 50% split of
having issues/not. There is a large reduction in the population of men with 
back issues in comparison.


# Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.

## Thoughts


## Code and Output
```{r}
backpack %>% 
  #mutate(weight_ratio = backpack_weight/body_weight) %>% 
  ggplot(aes(x = body_weight,
             y = backpack_weight)) +
  geom_point() +
  facet_grid(back_problems ~ sex) +
  my_theme
```
```{r}
max_ratio <- round(max(backpack$backpack_weight/backpack$body_weight), 2)

backpack %>% 
  mutate(weight_ratio = backpack_weight/body_weight,
         back_problems = if_else(back_problems == 1, "Back Issues", "No Issues")) %>% 
  ggplot() +
  geom_histogram(aes(x = weight_ratio,
                     fill = factor(sex),
                     ), colour = "black",
                 show.legend = FALSE) +
  facet_grid(back_problems ~ sex) +
  scale_fill_brewer(palette = "Dark2") +
  #scale_x_continuous(breaks = max_ratio * seq(0.1, 1, 0.1)) +
  my_theme +
  labs(title = "Ratio of bags to body weight and Wheter Issues Arise",
       y = "Count",
       x = "Weight Ratio (bags/body)")
```


## Discussion
The first scatter plot tends to tell limits information in terms of trends. The
histograms do show that generally more issues occur when there is a higher ratio
of bag to body weight.



## 3 Extensions


# Question 1.

Does reported backpain differ across the year groups? Ignore year 0 in your data.

## Thoughts
Can complete similar to before but will need to replace sex with year. Might also
need to check the number of pupils in each year.

## Code and Output

```{r}
backpack %>% 
  group_by(back_problems, year) %>% 
  summarise(count_num = n()) %>% 
  group_by(year) %>% 
  mutate(percent = round(100*count_num/sum(count_num), 0)) %>% 
  mutate(back_problems = if_else(back_problems == 1, "Issue", "No Issue")) %>% 
  ggplot(aes(x = year,
             y = percent,
             fill = factor(back_problems))) +
  geom_col() +
  scale_fill_manual(values = c("Purple", "Orange"))+ #scale_fill_distiller(palette = "Dark2") +
  geom_text(aes(label = paste0(percent, "%")),
            position = position_stack(vjust = 0.5)) +
  my_theme +
  scale_x_continuous(breaks = seq(0, 6, 1)) + 
  labs(title = "Students with Back Problems For each Year Group",
       y = "Percentage",
       x = "Year Group",
       fill = "Back Problems")
```

```{r}
backpack %>%
  group_by(year) %>% 
  summarise(num_pupils = n()) %>% 
  ggplot(aes(x = year,
         y = num_pupils)) +
  geom_col() +
  my_theme
```


## Discussion
The year groups from 1 to 5 have issues whereas 0 and 6 have no issues. However
For the number of pupils in years 0 and 6 are very low when compared to the other
years. Therefore if there were more there is the possibility that this would be
around 30% similar to other years.

# Question 2.

Is there a difference between how heavy the bags those in different years carry?

## Thoughts
Could do a histogram for each year with a distribution of weight.

## Code and Output
```{r}
backpack %>% 
ggplot(aes(x = backpack_weight)) +
  geom_histogram(binwidth = 1,
                 aes(fill = year,
                 ), colour = "black",
                 show.legend = FALSE) +
  labs(title = "Distribution of Backpack Weight",
       x = "Backpack Weight (lbs)") +
  facet_wrap(~ year)+
  scale_y_continuous(expand = c(0,0)) + #breaks = seq(1, max(backpack$backpack_weight), 2)) +
  my_theme
  
```

## Discussion
Majority of years show a similar skew to back weights of around 10lbs. The 
distribution of bag weight it more spread out for year 5 in comparisson to 
other years.