---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
# Question 1
```{r}
# Load in data
code_clan_tweets <- read_csv("data/code_clan_tweets.csv")
```

```{r}
# Rows and columns
dim(code_clan_tweets)
# Names of the columns
names(code_clan_tweets)
```
```{r}
# Look at a summary of the data
glimpse(code_clan_tweets)
```
```{r}
#check for errors in columns
code_clan_tweets %>% 
  summarise(across(.fns = ~sum(is.na(.x))))
```

# Question 2
```{r}
code_clan_tweets %>% 
  filter(is_quote != TRUE) %>% 
  summarise(number_of_favourites = sum(favorite_count))
```


# Question 3
```{r}
code_clan_tweets %>%
  filter(is_quote != TRUE) %>% 
  group_by(source) %>% 
  summarise(mean_count = mean(retweet_count, na.rm = TRUE))
  
```

# Question 4
```{r}
code_clan_tweets %>%
  mutate(media_type = if_else(is.na(media_type), "text", media_type)) %>% 
  group_by(media_type) %>% 
  summarise(count_of_likes = sum(favorite_count))
```

# Question 5
```{r}
code_clan_tweets %>% 
  summarise(mean_length = mean(display_text_width, na.rm = TRUE))
```

```{r}
code_clan_tweets %>% 
  mutate(tweet_length = nchar(text)) %>% 
  summarise(mean_tweet_length = mean(tweet_length))

```

# Question 6
```{r}
code_clan_info <- read_csv("data/code_clan_info.csv")
```
```{r}
glimpse(code_clan_info)
```
code_clan_info = 234x15
code_clade_tweets = 234 x 27
primary key = tweet_id
expected 1:1 relationship
expected size = 234 x 15+26

```{r}
code_clan_joined <- left_join(code_clan_tweets, code_clan_info, 
                              by = c("tweet_id" = "tweet_id"))

code_clan_joined
```
# Question 7
```{r}
codeclan_hashtags <- code_clan_joined %>%
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  filter(!(is.na(hashtags))) %>%
  select(tweet_id, hashtags)

codeclan_hashtags
  
```
# Question 8
```{r}
# Finding the "c(" using str_detect and str_sub
codeclan_hashtags %>%
  mutate(found_with_detect = str_detect(hashtags, "c\\(")) %>% 
  mutate(found_with_sub = (str_sub(hashtags, 1, 2) == "c("))

```

# Question 8
```{r}
# Method 1 - Check tweets which contain "Edinburgh"
code_clan_joined %>% 
  summarise(contains_pattern = sum(
    str_detect(text, "[Ee][Dd][Ii][Nn][Bb][Uu][Rr][Gg][Hh]")))

# Method 2 - Using string to lower
code_clan_joined %>% 
  mutate(text = str_to_lower(text)) %>% 
  summarise(contains_pattern = sum(str_detect(text, "edinburgh")))

code_clan_joined %>% 
  summarise(contains_pattern = sum(
    str_detect(text, "[Ee][:alpha:]{7}[Hh]")))

# Method below is not quite working
# code_clan_joined %>% 
#   mutate(contains_pattern = (
#     str_detect(text, "[Ee][:alpha:]{7}[Hh]"))) %>% 
#   filter(contains_pattern == TRUE) %>% 
#   select(contains_pattern, text)
```

Twitter User name guidelines:
Your username cannot be longer than 15 characters. Your name can be longer 
(50 characters) or shorter than 4 characters, but usernames are kept shorter 
for the sake of ease.
A username can only contain alphanumeric characters (letters A-Z, numbers 0-9)
with the exception of underscores, as noted above. Check to make sure your 
desired username doesn't contain any symbols, dashes, or spaces.



```{r}
username_pattern <- "@[_[:alnum:]]{4,50}"
users_tweet <- code_clan_joined %>% 
  select(text) %>% 
  mutate(tweeted_users = str_extract_all(text, username_pattern))
  
```




