---
title: "Week 11- Day 3 - Clustering"
output: html_notebook
---

# Load in libraries
```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
library(broom)
library(GGally)
```


Clustering homework
You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings.



```{r}
mall_customer <- read_csv(here::here("data/mall_customers.csv")) %>% 
  rename_with(.fn = ~str_replace(.,"\\(.*", "")) %>% 
  janitor::clean_names()
```

```{r}
skimr::skim(mall_customer)
```
## Thoughts
Standardise the variables and remove the customer id column

## Code
```{r}
mall_scale <- mall_customer %>% 
  select(-c(customer_id)) %>% 
  mutate(across(where(is.numeric), .fns = scale),
         gender = if_else(gender == "Male", 1, 0))
```

```{r}
mall_scale_no_gender <- mall_customer %>% 
  select(-c(customer_id, gender)) %>% 
  mutate(across(where(is.numeric), .fns = scale))
```




```{r}
# Quick check for standardisation
mall_scale %>% 
  select(where(is.numeric)) %>% 
  summarise(across(.fns = list(mean = mean,
                                      sd = sd)))

```


```{r}
mall_scale %>% 
  summarise(across(.fns = ~sum(is.na(.x))))
```




```{r}
mall_scale %>% 
  ggpairs()
```





We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers.


```{r}
max_k <- 20

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(mall_scale, .x, nstart = 25)), # created k-cluster object in each row
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, mall_customer)
  )
```

```{r}
clusterings <- k_clusters %>% 
  unnest(glanced)


clusterings %>% 
  ggplot(aes(k, tot.withinss)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:max_k)
```

```{r}
# Elbow/Silhouette of mall with gender 
fviz_nbclust(mall_scale, kmeans, method = "wss", nstart = 25)
fviz_nbclust(mall_scale, kmeans, method = "silhouette", nstart = 25)
fviz_nbclust(mall_scale, kmeans, method = "gap_stat", nstart = 25)
```


```{r}
# Elbow /slihouette of mall no gender
fviz_nbclust(mall_scale_no_gender, kmeans, method = "wss", nstart = 25)
fviz_nbclust(mall_scale_no_gender, kmeans, method = "silhouette", nstart = 25)
fviz_nbclust(mall_scale_no_gender, kmeans, method = "gap_stat", nstart = 25)
```

## Discussion
FOr the clusterning with the gender field (1 = male and 0 = female), the 
elbow and silhouette plots are similar. However for the gap plot, they are 
different. Due the variation 2 and 6 cluster recommendations, the value of 
4 will be used.


Perform k-means clustering and chose a value of k.

```{r}
cluster_with_gender <- mall_scale %>% 
  kmeans(centers = 6, nstart = 25)

cluster_with_no_gender <- mall_scale_no_gender %>% 
  kmeans(centers = 6, nstart = 25)
```

```{r}
mall_gender <- augment(cluster_with_gender, mall_customer)
mall_no_gender <- augment(cluster_with_no_gender, mall_customer)
```




Visualise the clustering for your chosen value of k.

```{r}
mall_gender %>% 
  ggpairs(column = 2:5, progress = FALSE, 
          mapping = aes(colour = .cluster), legend = 1)
```

```{r}
mall_no_gender %>% 
  ggpairs(column = 3:5, progress = FALSE,
          aes(colour = .cluster), legend = 1)
```


Do you think the clustering seems a good fit for this data?

Since we obtained different values of recommendation of clusters, this
may not be the best for k-means. However the recommended clusters of
6 with no gender could indicate otherwise.
The visualisations, do however indicate that ethere could be some overlap
on one of the planes (for example annual income vs spending for clusters
2 and 5). 
This is again shown in the means of the data where there are some values which
overlap.
The annual income vs spending shown better "group" for data
compared to the age which can have larger ranges. Which may make this less
suitable.

```{r}
mall_no_gender %>% 
  group_by(.cluster) %>% 
  summarise(across(where(is.numeric), .fns = mean),
            perc_male = 100*sum(gender == "Male")/n(),
            num_female = 100*sum(gender == "Female")/n(),
            perc_data = 100*n()/nrow(.)) %>% 
  select(-customer_id)

```
```{r}
mall_gender %>% 
  group_by(.cluster) %>% 
  summarise(age_range = paste(min(age), "to", max(age)),
            across(where(is.numeric), .fns = mean),
            perc_male = 100*sum(gender == "Male")/n(),
            perc_female = 100*sum(gender == "Female")/n(),
            perc_data = 100*n()/nrow(.)) %>% 
  select(-customer_id)
```


```{r}
bind_rows("has_gender" = glance(cluster_with_gender),
          "no_gender" = glance(cluster_with_no_gender))
```



Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the ‘Segmentation & clustering intro’ lesson).

Using gender-
CLuster 1 - Is 11.5% in data set. has 43.5% male/56.5% female.
            mean age is 25 with an income of 25k and high spending score of
            77.
Cluster 6 - Is 10.5 % of population, has 38% males and 62% female,
            mean age is 46 with a annumal income of 26 but much lower score of
            19.


