---
title: "week 2 - Day 1 Homework"
output:
  html_document:
    df_print: paged
---
# Q1.1 - Joins
## Read in the CSV files and packages
### Packages
```{r}
library(tidyverse)
library(janitor)
```
### q1 - Read csv's
```{r}
card_data <- read_csv("data/CardBase.csv") %>% 
  clean_names()
customer_data <- read_csv("data/CustomerBase.csv") %>% 
  clean_names()
fraud_data <- read_csv("data/FraudBase.csv") %>% 
  clean_names()
transaction_data <- read_csv("data/TransactionBase.csv") %>% 
  clean_names()
```
### Q2-
join card details and customer details by card id- so that all record
of card details and any matching records in customer details are kept.

customer_data = 5674x4
card_data = 500x4

expected output= (500(plus matches if any)) x (4 + (3 from customer_data))

result shows a 1:1 relationship for customer_id

```{r}
left_join(card_data, customer_data, by = c("cust_id" = "cust_id"))

```

### Question 3-
Join fraud details with transaction details
keep - all rows in both tables

transaction_data = 10,000 x 5
fraud_data = 109 x 2

expected output - (10,000 + additional matches) x 2+4

results- tell you that 1:1 relationship between transaction_id
all transactions in the fraud data base are accounted for in the transaction_data
```{r}
full_join(fraud_data, transaction_data, by = c("transaction_id" = "transaction_id"))
```

### Question 4
Join card details with transaction details
keep - rows from first match the second are returned
  only return results from 1st table once
  
card_data = 500x4
transaction_data = 10000 x 5
relationship - card:transaction = 1:many

result - 10000 x 3+5

```{r}
right_join(card_data, transaction_data, by = c("card_number" = "credit_card_id"), keep = FALSE)
card_data
transaction_data
```

```{r}
right_join(transaction_data, card_data, by = c("credit_card_id" = "card_number"), keep = FALSE)
```

# 1.2
# Question 5
Read in data sets
```{r}
hats <- read_csv("data/hat_observations.csv")
```

```{r}
hat_separated <- hats %>% 
  separate(observation,
           into = c("hat_colour", "hat_type"),
           sep = ",")

hat_separated
```

### Question 6
```{r}
hat_dates <- hat_separated %>% 
  unite(date,
        c(day, month, year),
        sep = "/") %>% 
  filter(hat_type == "beret") %>% 
  slice_max(observation_count)

hat_dates
```

# Extension
### Q1

cand_number = cust_id, card_number = credit_card_id, 
transaction_id = transaction_id

```{r}
left_join(card_data, customer_data, by = c("cust_id" = "cust_id")) %>% 
  left_join(transaction_data, by = c("card_number" = "credit_card_id")) %>% 
  right_join(fraud_data, by = c("transaction_id" = "transaction_id"))
```

### Question 2
```{r}
exam_score <- read_csv("data/exam_scores.csv")
```

Read in exam_scores and transform it into long format with two new columns exam_question and score. Then, using separate and select, remove superfluous information from the values in exam_question

```{r}
# Don't need separate and select?
exam_score %>% 
  pivot_longer(cols = starts_with("exam"),
               names_to = "exam_question",
               names_prefix = "exam_Q",
               values_to = "score")
```

```{r}
# Completing as per the question
exam_score %>% 
  pivot_longer(cols = starts_with("exam"),
               names_to = "exam_question",
               values_to = "score") %>% 
  separate(exam_question, into = c("temp", "exam_question"),
           sep = "Q") %>% 
  select(-temp)
```

