---
title: "Probablility Homework"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)
```
```{r}
titanic <- read_csv("data/titanic.csv")
```

# Question
Calculate the conditional probabilities prob(survived∣crew) and prob(survived∣passenger) to settle this dispute.

```{r}
titanic <- titanic %>% 
  mutate(crew = case_when(
    str_detect(class, "crew|staff") ~ TRUE,
    TRUE ~ FALSE))
```
```{r}
crew_survived <- titanic %>%
  filter(survived == "yes", crew == TRUE)

passenger_survived <- titanic %>% 
  filter(survived == "yes", crew == FALSE)

crew_number = sum(titanic$crew)
passenger_number = nrow(titanic) - crew_number

crew_survived %>% 
  summarise(crew_and_sur_prob = n()/nrow(titanic),
            passe_and_surv_prob = nrow(passenger_survived)/nrow(titanic))

passenger_survived %>% 
  filter(survived == "yes", crew == FALSE) %>% 
  summarise(crew_and_sur_prob = n()/nrow(titanic))
  
```



```{r}



```



# 1.2 Probability Consolidation Questions
Today was pretty full-on! Here are some problems to help you consolidate what you learned. Feel free to work on paper or in R, whichever you are most comfortable with:

MVP - try four of the problems
Extension - try more than four!


## Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

Probability = 2/3 = 66.67%

```{r}
rolldie(1) %>% 
  summarise(prob_less_than_5 = sum(X1<5)/n())

```



## Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?

Sample space = die_sides^3 = 6^3 = 216

```{r}
rolldie(3) %>% 
  nrow()
```


# Question 3.
In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals 5, 6 or 7)?
what is the probability of this event?
what assumptions do we apply in answering part ii?
Hint
For part i, rowSums(.) may help you setup up the necessary random variable total (or you can use pivot_longer())

```{r}
four_die_outcome <- rolldie(4) %>% 
  filter(rowSums(.) %in% c(5, 6, 7))

rolldie(4) %>% 
  summarise(prob_of_roll = nrow(four_die_outcome) / n())

# Assumptions applied is that all outcomes are as likely to happen as another.
```



# Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

Hint
This is an arrangement where order matters. Of all the possible arrangements, how many are correct?

>Num dist = N!/(N-r)! = 5!/(5 - 5)! = 120
Correct order = 1 only
Prob = 1/120 = 0.833%


```{r}
height <- c(175, 170, 185, 145, 160)

height_order <- sort(height, TRUE)


as_tibble(permutations(n = length(height), r = 5, v = height, 
                       repeats.allowed =  FALSE
          )) %>% 
  unite("merged", 1:length(height), remove = FALSE) %>% 
  summarise(probability = sum(str_c(height_order, collapse = "_") == merged)/n())
  


```



Question 5.
I roll six dice:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
Hint
Have a look at the isin() function in the prob package. For example, to filter all rows containing 6, 1, 2 in that order, you could use isin(., c(6, 1, 2), ordered = TRUE)

>1- Permutation
num_dist = N!/r!(N-r)!= (6)!/6!(6 - 6)! = 1 => probability = 1/6^6= 2.14e-3%



```{r}
dice_output <- c(6, 5, 4, 3, 2, 1)

rolldie(6) %>% 
   unite("merged", 1:6, remove = FALSE) %>% 
  summarise(probability = sum(str_c(dice_output, collapse = "_") == merged)/n())
  
sum(isin(rolldie(6), dice_output, ordered = TRUE))/nrow(rolldie(6))
```



>2- num_dist = N!/(N-r)!= (6)!/(6 - 6)! => probability = 720/6^6 = 1.54%

```{r}
permute <- as_tibble(permutations(6, 6, v = 1:6)) %>% 
  unite("permutation_list", 1:6, remove =TRUE)

rolldie(6) %>% 
  unite("merged", 1:6, remove = FALSE) %>% 
  filter(merged %in% permute$permutation_list) %>% 
  summarise(probability = n()/nrow(rolldie(6)))
  

sum(isin(rolldie(6), dice_output))/nrow(rolldie(6))
```



Question 6.
If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

Hints
Investigate the cards() function in the prob package, if you’d like to try this in R (make a deck without jokers).
You could think about adding your own black_card random variable to the sample space, which would be TRUE if the suit is ‘Spade’ or ‘Club’, and FALSE otherwise.

Pr(spade | black)

No. black cards = 26, N of spades = 13,

50% chance

```{r}
black_cards <- cards(jokers = FALSE) %>% 
  filter(suit == "Club" | suit == "Spade")

cards(jokers = FALSE) %>% 
  filter(suit == "Spade") %>% 
  summarise(prob_of_spade = n()/nrow(black_cards))
```

