---
title: "Week 5 day 1"
output: html_notebook
---

# Read in libraries
```{r}
library(tidyverse)
library(CodeClanData)
library(janitor)
```

```{r}
revenue <- qb_revenue_breakdown %>% clean_names()
monthtly_sales <- qb_monthly_sales %>% clean_names()
competitors <- qb_competitors %>% clean_names()
device_data <- qb_device_data %>%  clean_names()
```

# Part 1

## Question 1.
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
revenue %>% 
  ggplot(aes(x = year, y = revenue)) +
  geom_col(aes(fill = product))
```





## Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).


```{r}
monthtly_sales %>% 
  filter(cashflow == "Kwikbit Unit 1 Sales") %>% #as.numeric(format(date, "%Y")) == 2019  & 
  ggplot(aes(x = date,
             y = amount)) +
  geom_line()
```


## Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
monthtly_sales %>% 
  filter(cashflow != "Kwikbit Unit 1 Sales") %>% #as.numeric(format(date, "%Y")) == 2019  & 
  ggplot(aes(x = date,
             y = amount)) +
  geom_line(aes(colour = cashflow))
```



## Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.


```{r}
competitors %>% 
  ggplot(aes(x = year,
             y = revenue,
             fill = company)) +
  geom_area()
```


## Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
competitors %>% 
  ggplot(aes(x = year,
             y = revenue,
             colour = company)) +
  geom_line() +
  geom_point()
```


## Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}
device_data %>% 
  mutate(time = hours + mins/60) %>% 
  group_by(id, device) %>% 
  mutate(step_count = cumsum(counts)) %>% 
  ggplot(aes(x = time,
             y = step_count)) +
  geom_line(aes(colour = device)) +
  facet_wrap(~ id)

```



# Part 2
Question 1.
Take the plots that you produced in part one and now polish them by:

Adding appropriate labels
Changing the scales and coordinates when appropriate.
Applying a unified theme, which is described below:
Graphs should have white backgrounds, and use colour sparingly.
There should be faint grid lines.
Font sizes should be ~12pt although titles should be slightly larger and axis labels can be slightly smaller.
All plots should use colours from the following company colour scheme.


col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")


```{r}
theme_quickbit <- function(
    title_text_size = 12,
    label_text_size = title_text_size - 1,
    col_or_fill = "Fill")
{
  # col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
  #   #scale_fill_manual(values = col_scheme) +
  #   if (col_or_fill == "Fill"){
  #   scale_fill_manual(values = col_scheme)
  # }else{
  #     scale_colour_manual(values = col_scheme)
  #   } +
  theme_bw() +
  theme(axis.text= element_text(size = label_text_size,
                                vjust = 0.5),
        plot.title = element_text(size = title_text_size,
                                  hjust = 0.5),
        panel.background = element_rect(fill = "White"),
        panel.grid = element_line(colour = "grey92"))
    
}
```


## Question 1.
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
revenue %>% 
  ggplot(aes(x = year, y = revenue)) +
  geom_col(aes(fill = product)) +
  theme_quickbit()+
  scale_fill_manual(values = col_scheme) +
  labs(title = "Revenue from Products Each Year",
       x = "\nYear",
       y = "Revenue (£)\n",
       fill = "Product Type")
```





## Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).


```{r}
monthtly_sales %>% 
  filter(cashflow == "Kwikbit Unit 1 Sales") %>% #as.numeric(format(date, "%Y")) == 2019  & 
  ggplot(aes(x = date,
             y = amount)) +
  geom_line() +
  labs(title = "Monthly Sales of Kwikbit Unit 1",
       subtitle = "August 2018 to July 2019",
       x = "\nMonth",
       y = "Revenue (£)\n")+
  theme_quickbit()+
  scale_x_date(date_breaks = "1 month", date_labels =  "%b") 
```


## Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
monthtly_sales %>% 
  filter(cashflow != "Kwikbit Unit 1 Sales") %>% #as.numeric(format(date, "%Y")) == 2019  & 
  ggplot(aes(x = date,
             y = amount)) +
  geom_line(aes(colour = cashflow), 
            size = 2) +
  labs(title = "Monthly Sales of Kwikbit Unit 1",
       subtitle = "August 2018 to July 2019",
       x = "\nMonth",
       y = "Revenue (£)\n",
       colour = "Cash Flow") +
  theme_quickbit()+
  scale_colour_manual(values = col_scheme) +
  scale_x_date(date_breaks = "1 month", date_labels =  "%b") +
  scale_y_continuous(limits = c(0, 3000))
```



## Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.


```{r}
competitors %>% 
  ggplot(aes(x = year,
             y = revenue * 1e-6,
             fill = company)) +
  geom_area() +
  labs(title = "Annual Sales of Personal Fitness Trackers",
       x = "\nYear",
       y = "Revenue (£Million)\n",
       fill = "Company") +
  theme_quickbit()+
  scale_fill_manual(values = col_scheme) +
  expand_limits(y = c(0, NA)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7))
```


## Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
competitors %>% 
  ggplot(aes(x = year,
             y = revenue * 1e-6,
             colour = company)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  labs(title = "Annual Sales of Personal Fitness Trackers",
       x = "\nYear",
       y = "Revenue (£Million)\n",
       colour = "Company") +
  theme_quickbit()+
  scale_colour_manual(values = col_scheme)
```


## Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}
device_data %>% 
  mutate(time = hours + mins/60) %>% 
  group_by(id, device) %>% 
  mutate(step_count = cumsum(counts)) %>% 
  ggplot(aes(x = time,
             y = step_count * 1e-3)) +
  geom_line(aes(colour = device)) +
  labs(title = "Step Count for Individuals with Each Device",
       x = "\nTime (hr)",
       y = "Step Count (k)\n",
       colour = "Device") + 
  theme_quickbit()+
  facet_wrap(~ id)

```